The effects of binarity on planet occurrence rates measured by transit surveys

### 2018-01-30 paper/main.tex
further minor edits

\title{ The effects of binarity on planet occurrence rates measured by transit 
surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%
Wide-field surveys for transiting planets, such as the NASA {\it Kepler}
and {\it TESS} missions, are usually conducted without knowing which stars
are actually binaries. Unresolved and unrecognized binary stars give rise to 
systematic errors in planet occurrence rates, including misclassified planets 
and miscounts in the number of searched stars. The individual errors can have 
different signs, making it difficult to anticipate the net effect on planet 
occurrence rates. Here we use simplified models of signal-to-noise limited 
transit surveys to try and clarify the situation. We derive a formula for the 
apparent occurrence rate density measured by an observer who falsely assumes 
all stars are single. The formula depends on the binary fraction; the 
mass function of the secondary stars; and the true occurrence of planets 
around primaries, secondaries, and single stars. It also takes into account 
the Malmquist bias by which binaries are over-represented in flux-limited 
samples. Application of the formula to an idealized {\it Kepler}-like survey 
shows that for planets larger than $2r_\oplus$, the net systematic error is of 
order 10\%. For smaller planets the errors are potentially larger: the 
occurrence of Earth-sized planets could be overestimated by as much as a 
factor of two. One consequence is that unrecognized binaries cannot account 
for the apparent discrepancy between the hot Jupiter occurrence rates measured 
by transit and RV surveys. We also show that if high-resolution imaging 
reveals a transit host star to be a binary, the planet is usually more likely 
to orbit the primary star than the secondary star.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

One of the goals of exoplanetary science is to establish how common,
or rare, are planets of various types.  Knowledge of planet occurrence
rates is helpful for inspiring and testing theories of planet
formation, designing the next generation of planet-finding surveys,
and simply satisfying our curiosity about other worlds.  One method
for measuring occurrence rates is to monitor the brightnesses of many
stars over a wide field, seeking evidence for planetary transits.
Measuring occurrence rates using this method was the highest priority
of the NASA {\it Kepler} mission.  Great strides have been made in the
analysis of {\it Kepler} data, including progress toward the goal of
determining the fraction of Sun-like stars that harbor Earth-like
planets~\citep{
  youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
  foreman-mackey_exoplanet_2014,burke_terrestrial_2015}

A lingering concern in occurrence rate studies is that in most cases,
investigators have assumed that all of the sources of light that were
monitored are single stars~\citep[\textit{e.g.},][]{
  howard_planet_2012,fressin_false_2013,foreman-mackey_exoplanet_2014,
  dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of
them are unresolved multiple-star systems, especially binaries.
Unrecognized binaries cause numerous systematic errors in the
planetary occurrence rates.  For example, when there is a transiting
planet around a star in a binary, the additive constant light from the
second star reduces the fractional loss of light due to the planet.
This ``flux dilution'' makes transit signals harder to detect and
lowers the number of detections.  On the other hand, in a binary there
two opportunities to detect transiting planets, which could increase
the overall number of detections.

At the outset of this study it was not clear to us whether the neglect
of binaries was a serious issue at all, or even whether the net effect
of all the errors is positive or negative.  The goal of this study was
to clarify the various sources of error and provide a framework for
dealing with these issues.  In this spirit, most of our models are
idealized and analytic, and we do not attempt a detailed correction of
the results from {\it Kepler} or any other real transit survey.
However we can estimate the order of magnitude of the effects,
assuming the survey is signal-to-noise limited and given a model for
the true planet occurrence rate.

This paper is organized as follows.  The next section enumerates the
various errors that arise from unrecognized binaries.  Then, in
Section~\ref{sec:simplest}, we develop an idealized model of a transit
survey in which all planets have identical properties, and all stars
are identical except that some fraction are in binary systems.  This
simple model motivates the derivation of a general formula, given in
Section~\ref{sec:general_formula}, that allows for more realistic
stellar and planetary populations.  We use this formula in
Section~\ref{sec:more_complicated} to explore more complicated but
nevertheless still analytic models.  In Section~\ref{sec:discussion}
we discuss the errors due to unrecognized binaries for some specific
cases of current interest: the occurrence of Earth-like planets; the
apparent discrepancy between hot-Jupiter occurrence rates in different
surveys; and the shape of the ``evaporation valley'' in the radius
distribution of planets that was brought to light by
\citet{fulton_california-_2017}.  We review all the results in
Section~\ref{sec:conclusion}.

@@

The astronomers then assume that all stars are single.  In particular
they do not have accurate enough parallaxes to tell that some of the
stars are apparently overluminous. 
They want to compute the number of planets with size $r$ per star of mass $M$.
If the total number of such stars for which the planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are both 
large, then the astronomers' estimate for the occurrence rate ($\Lambda$) is 
simply
\begin{equation}
\Lambda(r,M) = \frac{N_{\rm det}(r,M)}{N_\star(r,M)}
                    \times \frac{1}{p_{\rm tra}(r,M)},
\label{eq:occ_rate_simple}
\end{equation}
where $p_{\rm tra}$ is the geometric transit probability, needed to
account for the fact that most planetary orbits are not aligned close
enough with our line of sight to produce transits.

@@

We will focus exclusively on the subset of problems that arise from
the fact that many stars exist in gravitationally bound binary
systems.  Even with this narrow focus, there are numerous sources of
error.  All three of the quantities in
Equation~\ref{eq:occ_rate_simple} are subject to
observational bias:
\begin{enumerate}
%    
    \item The number of detections, $N_{\det}$, is actually the number of 
    detected planets that {\it appear} to have size $r$, orbiting stars that 
    {\it appear} to have mass $M$.
    Whenever the planet-hosting star is part of a binary,
%    
    \begin{itemize}
        \item the planet's size will be misclassified because of the reduction
        in the amplitude of the photometric signal;
%        
        \item the host star's properties could be misclassified because its 
        light is combined with a second star of a different spectral type.
%        
    \end{itemize}
%    
    \item The apparent number of stars that were searched, $N_\star$,
    is biased
%    
    \begin{itemize}
%        
        \item toward lower values, because it does not include all of the
        secondary stars that were searched for transiting planets.
%        
        \item toward higher values, because some of the stars that
        appeared to be suitably small and bright to detect the desired
        type of planet are in fact binaries for which the amplitude of
        the photometric signal would be reduced to an undetectable
        level.
%        
    \end{itemize}
%    
    \item The transit probability $p_{\rm tra}$, which scales with the
    stellar mean density as $\rho^{-1/3}$, is biased because the
    planet-hosting star could be misclassified.
%    
\end{enumerate}

@@

The other problem is an observational effect.  Even after the
astronomers learn about binaries and attempt to correct for their
presence, they must realize that the ratio of binaries to single stars
in the sample will differ from that in a volume-limited sample due to
a type of Malmquist bias.  Binaries have a higher total luminosity
than either the primary or secondary star would have on its own.  This
means that the binaries are searchable for transit signals of a given
amplitude at greater distances from the Earth.  The binaries in a
sample of apparently searchable stars are therefore drawn from a
larger search volume than the single stars.

% JNW: Let's remember, when discussing Kepler, to point out that it's
% not really a SNR or flux limited survey, because of the
% preselection. This would need to be dealt with in a realistic
% treatment.

% JNW: Let's also remember to say somewhere that we do not deal with
% period distributions none of these effects mess up the period.

@@

Given all of the confusing and opposing sources of error, we will
proceed in stages. We will start from a barebones model in which
everything can be written down on the back of a napkin, and build up
to an analytic model allowing for generality in the distribution of
the binaries and the planets they host.  We consider only the
corrections to the occurrence as a function of planetary radius, and
not the orbital period (the other key variable in transit studies),
because when multiple transits are detected the period can be directly
measured regardless of whether the host star is single or part of a
binary.

@@

We can now understand that the observers are unwittingly
reporting an {\it apparent} occurrence rate $\Lambda\a(r\a)$ as
a function of apparent radius.
The apparent occurrence rate is the same as the {\it true} occurrence rate for 
transit signals of 
amplitude $\delta_{\rm obs} = (r\a/R\a)^2$, \textit{i.e.}, the number of 
detections ($N_{\rm det}$) of signals of amplitude $\delta_{\rm obs}$, divided 
by the number of sources $N_\star$ from which such a signal could be detected.

@@

To compute the number of detected planets, we consider the volumes within 
which a given signal could be detected. At a fixed signal-to-noise floor, 
there is a maximum searchable 
distance~\citep{pepper_using_2003,pepper_searching_2005}.
From Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
\begin{equation}
d \propto \delta_{\rm obs} \cdot L_{\rm 
    sys}^{1/2}.
\end{equation}
Assuming that stars are uniformly distributed in space, the number 
of searchable stars $N_\star$ is then proportional to
\begin{equation}
N_\star \propto n \delta_{\rm obs}^3 L_{\rm 
    sys}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
systems.
We neglect the dependence of $n$ on stellar type.

@@

The searchable volumes for this example are illustrated in 
Figure~\ref{fig:model_1_volumes}.
At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
with $d<d_0$ are searchable.
Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
However, in this example no such systems exist; all planets in twin binaries 
have true radii $r=r\p$, and so are observed with apparent radii 
$r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.
At an apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets with 
true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no such systems 
in this model.

@@

The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
is the number of unresolved point-sources on sky that the observer thinks are 
searchable, $N_\star$.
From the definition of $\mu$,
\begin{equation}
N_\star(r\a) = N_\star^0(r\a) \times (1 + \mu)
\label{eq:apparentlysearchable_to_searchable}
\end{equation}
relates the number of apparently searchable point-sources to the number of 
searchable singles.
From the discussion above, it should be clear that there are in fact
$N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars at any given $r\a$; the 
observers are under-counting.

Using Equation~\ref{eq:apparent_rate_density}, the apparent rate density 
computed when ignoring binarity is
\begin{align}
\Gamma\a(r\a) = 
\frac{1}{1+\mu} Z_0 \cdot
\delta(r\a-r\p)  +
\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
\delta\left(r\a-\frac{r\p}{\sqrt{2}} \right).
\label{eq:model_1_apparent_rate_density}
\end{align}
The number of searchable singles at a given apparent radius, 
$N_\star^0(r\a)$, makes no appearance.
The observer has erred in Equation~\ref{eq:model_1_apparent_rate_density} by 
under-counting the number of searchable stars at any apparent radius, and by
inferring incorrect planet radii in binary systems.

@@

To assess the severity of these errors, we must assume both a binary fraction, 
and also the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,Z_2$).
For the former,~\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
sample that are multiple'', which we simplistically take to be fraction of 
systems in a volume-limited sample that are binaries:
\begin{equation}
{\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
\end{equation}
Of course not all of these are binaries are close to being ``twin'' binaries 
as we have assumed in our simple calculation.
Perhaps only a tenth of them have pairs of stars close enough
in their basic properties to produce errors as significant as those
we have been considering.  Thus, an appropriate estimate
for the binary fraction is of order $0.05$.
The ratio of the apparent to single star rate densities,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r},
\end{equation}
can then be thought of as a ``correction factor''.
At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
0.05~(0.10).
All together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is characteristic
of many of our more complicated models, as well.

An alternative assumption is that secondaries do not host planets. In that 
case, the correction to the rate density at the true planet radius becomes 
$X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
Although the secondaries certainly should have planets, 
the fact that $\Gamma\a/\Gamma_0$ is sensitive to the relative number 
of planets per single, primary, and secondary will also become
important as we proceed.

@@

A simple extension to the previous example helps distinguish 
between the apparent and underlying planet populations.
Consider now a universe that is the same as that of 
Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
while the other half have radii $r\p/\sqrt{2}$.
The rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where as before $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to 
secondaries, and the $Z_i$'s are the number of planets per star of each type.

Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
apparent rate density can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
There are now three different sizes of detected planets.
The important qualitative point is that at $r\a = 
r\p/\sqrt{2}$, two populations contribute.
The first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
Just as with Equation~\ref{eq:apparentlysearchable_to_searchable}, we benefit 
from a cancellation of $N_\star^0(r\a)$ terms, leaving only the $\mu$ weights.
Generally, at any given apparent radius, there will be contributions
from both single, primaries, and secondaries~---~but the relative weights
between these contributions will depend on the underlying occurrence rates.

@@

A derivation of Equation~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; its qualitative features are as follows.
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of different planetary and stellar properties, as determined
by the mass ratio $q$ of each binary.
This corresponds to true planet radii and stellar masses 
$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
secondaries.
These contributions are then integrated over the mass ratio distribution 
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
further below. Finally, the latter term in the apparent rate density of 
secondaries comes from a correction for the overestimated transit probability.

>>>>

\title{ The effects of binarity on planet occurrence rates measured by
transit surveys}
%
\correspondingauthor{L. Bouma}
\email{luke@astro.princeton.edu}
%
\author{L. G. Bouma}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{K. Masuda}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
\author{J. N. Winn}
\affiliation{
    Department of Astrophysical Sciences,
    Princeton University,
    4 Ivy Lane, Princeton, NJ 08540, USA}
%
%
\begin{abstract}
%

Wide-field surveys for transiting planets, such as the NASA
{\it Kepler} and {\it TESS} missions, are usually conducted without
knowing which stars are binaries. Unresolved and unrecognized binary
stars give rise to systematic errors in planet occurrence rates,
including misclassified planets and miscounts in the number of
searched stars. The individual errors can have different signs,
making it difficult to anticipate the net effect on inferred
occurrence rates. Here we use simplified models of signal-to-noise
limited transit surveys to try and clarify the situation. We derive
a formula for the apparent occurrence rate density measured by an
observer who falsely assumes all stars are single. The formula
depends on the binary fraction; the mass function of the secondary
stars; and the true occurrence of planets around primaries,
secondaries, and single stars. It also takes into account the
Malmquist bias by which binaries are over-represented in
flux-limited samples. Application of the formula to an idealized
{\it Kepler}-like survey shows that for planets larger than
$2r_\oplus$, the net systematic error is of order 10\%. For smaller
planets the errors are potentially larger: the occurrence of
Earth-sized planets could be overestimated by as much as a factor of
two. One consequence is that unrecognized binaries cannot account
for the apparent discrepancy between hot Jupiter occurrence
rates measured by transit and RV surveys. We also show that if
high-resolution imaging reveals a transit host star to be a binary,
the planet is usually more likely to orbit the primary star than the
secondary star.
%
\end{abstract}
%
\keywords{
    methods: data analysis ---
    planets and satellites: detection ---
    surveys}
%
%

@@

One of the goals of exoplanetary science is to establish how common,
or rare, are planets of various types.  Knowledge of planet occurrence
rates is helpful for inspiring and testing theories of planet
formation, designing the next generation of planet-finding surveys,
and simply satisfying our curiosity about other worlds.  One method
for measuring occurrence rates is to monitor the brightnesses of many
stars over a wide field, seeking evidence for planetary transits.
Measuring occurrence rates using this method was the highest priority
of the NASA {\it Kepler} mission.  Great strides have been made in the
analysis of {\it Kepler} data, including progress towards measuring
the fraction of Sun-like stars that harbor Earth-like planets~\citep{
  youdin_exoplanet_2011,petigura_prevalence_2013,dong_fast_2013,
  foreman-mackey_exoplanet_2014,burke_terrestrial_2015}

A lingering concern in occurrence rate studies is that in most cases,
investigators have assumed that all of the sources of light that were
monitored are single stars~\citep[\textit{e.g.},][]{
  howard_planet_2012,fressin_false_2013,
  dressing_occurrence_2015,burke_terrestrial_2015}. In reality many of
them are unresolved multiple-star systems, especially binaries.
Unrecognized binaries cause numerous systematic errors in the
planetary occurrence rates.  For example, when there is a transiting
planet around a star in a binary, the additive constant light from the
second star reduces the fractional loss of light due to the planet.
This ``flux dilution'' makes transit signals harder to detect and
lowers the number of detections.  On the other hand, in a binary there
two opportunities to detect transiting planets, which could increase
the overall number of detections.

At the outset of this study it was not clear to us whether the neglect
of binaries was a serious issue at all, or even whether the net effect
of all the errors is positive or negative.  The goal of this study was
to clarify the various sources of error and provide a framework for
dealing with these issues.  In this spirit, most of our models are
idealized and analytic, and we do not attempt a detailed correction of
the results from {\it Kepler} or any other real transit survey.
Our goal is to estimate the order of magnitude of the effects,
assuming the survey is signal-to-noise limited, and given the true
underlying planet occurrence rates.

This paper is organized as follows.  The next section enumerates the
various errors that arise from unrecognized binaries.  Then, in
Section~\ref{sec:simplest}, we develop an idealized model of a transit
survey in which all planets have identical properties, and all stars
are identical except that some fraction are in binary systems.  This
simple model motivates the derivation of a general formula, given in
Section~\ref{sec:general_formula}, that allows for more realistic
stellar and planetary populations.  We use this formula in
Section~\ref{sec:more_complicated} to explore more complicated but
nevertheless still analytic models.  In Section~\ref{sec:discussion}
we discuss the errors due to unrecognized binaries for specific cases
of current interest: the occurrence of Earth-like planets; the
apparent discrepancy between hot Jupiter occurrence rates in different
surveys; and the shape of the ``evaporation valley'' in the planet
radius distribution that was brought to light by
\citet{fulton_california-_2017}.  We review all the results in
Section~\ref{sec:conclusion}.

@@

The astronomers then assume that all stars are single.  In particular
they do not have accurate enough parallaxes to tell that some of the
stars are apparently overluminous. 
They want to compute the number of planets with size $r$ per star of mass $M$.
If the total number of stars for which such planets could be detected
($N_\star$) and the number of detected planets ($N_{\rm det}$) are both 
large, then the astronomers' estimate for the occurrence rate ($\Lambda$) is 
simply
\begin{equation}
\Lambda(r,M) = \frac{N_{\rm det}(r,M)}{N_\star(r,M)}
                    \times \frac{1}{p_{\rm tra}(r,M)},
\label{eq:occ_rate_simple}
\end{equation}
where $p_{\rm tra}$ is the geometric transit probability, needed to
account for the fact that most planetary orbits are not aligned close
enough with our line of sight to produce transits.

@@

We will focus exclusively on the subset of problems that arise from
the fact that many stars exist in gravitationally bound binary
systems.  Even with this narrow focus, there are numerous sources of
error.  All three of the quantities in
Equation~\ref{eq:occ_rate_simple} are subject to
observational bias:
\begin{enumerate}
%    
    \item The number of planets, $N_{\det}$, is actually the number of 
    detected planets that {\it appear} to have size $r$, orbiting stars that 
    {\it appear} to have mass $M$.
    Whenever the planet-hosting star is part of a binary,
%    
    \begin{itemize}
        \item the planet's size will be misclassified because of the reduction
        in the amplitude of the photometric signal;
%        
        \item the host star's properties could be misclassified because its 
        light is combined with a second star of a different spectral type.
%        
    \end{itemize}
%    
    \item The apparent number of stars that were searched, $N_\star$,
    is biased
%    
    \begin{itemize}
%        
        \item toward lower values, because it does not include all of the
        secondary stars that were searched for transiting planets;
%        
        \item toward higher values, because some of the stars that
        appeared to be suitably small and bright to detect the desired
        type of planet are in fact binaries for which the amplitude of
        the photometric signal would be reduced to an undetectable
        level.
%        
    \end{itemize}
%    
    \item The transit probability $p_{\rm tra}$, which scales with the
    stellar mean density as $\rho^{-1/3}$, is biased because the
    planet-hosting star could be misclassified.
%    
\end{enumerate}

@@

The other problem is an observational effect.  Even after the
astronomers learn about binaries and attempt to correct for their
presence, they must realize that the ratio of binaries to single stars
in the searched sample will differ from that in a volume-limited
sample due to a type of Malmquist bias.  Binaries have a higher total
luminosity than either the primary or secondary star would have on its
own.  This means that the binaries are searchable for transit signals
of a given amplitude at greater distances from the Earth.  The
binaries in a sample of apparently searchable stars are therefore
drawn from a larger search volume than the single stars.

@@

Given all of the confusing and opposing sources of error, we will
proceed in stages. We start from a barebones model in which everything
can be written down on the back of a napkin, and build up to an
analytic model allowing for generality in the distribution of the
binaries and the planets they host.  We consider only corrections to
the occurrence as a function of planetary radius, and not orbital
period (the other key variable in transit studies), because when
multiple transits are detected the period can be directly measured
regardless of whether the host star is single or part of a binary.

@@

We can now understand that the observers are unwittingly reporting an
{\it apparent} occurrence rate $\Lambda\a(r\a)$, a function of
apparent radii.  The apparent occurrence rate is the same as the {\it
true} occurrence rate for transit signals of amplitude $\delta_{\rm
obs} = (r\a/R\a)^2$, but this latter quantity is typically not what
observers are interested in studying.

@@

To compute the number of detected planets, we consider the volumes within 
which a signal of a given depth could be detected. At a fixed signal-to-noise floor, 
there is a maximum searchable 
distance~\citep{pepper_using_2003,pepper_searching_2005}.
From Equation~\ref{eq:S_N_thresh}, this maximum searchable distance scales as
\begin{equation}
d \propto \delta_{\rm obs} \cdot L_{\rm 
    sys}^{1/2}.
\end{equation}
Assuming that stars are uniformly distributed in space, the number 
of searchable stars $N_\star$ is then proportional to
\begin{equation}
N_\star \propto n \delta_{\rm obs}^3 L_{\rm 
    sys}^{3/2},
\label{eq:N_searchable_prop}
\end{equation}
where $n$ is the number per unit volume of {\it e.g.}, single star, or binary 
systems.
We neglect the dependence of $n$ on stellar type.

@@

The searchable volumes for this example are illustrated in 
Figure~\ref{fig:model_1_volumes}.
At an apparent radius equal to the true radius ($r\a=r\p$), single stars 
with $d<d_0$ are by definition searchable.
Binaries with $r\a=r\p$ are also searchable, out to $\sqrt{2}d_0$. 
However, in this example no such systems exist; all planets in twin binaries 
have true radii $r=r\p$, and so are observed with apparent radii 
$r\a=r\p/\sqrt{2}$, out to $d_0/\sqrt{2}$.
At an apparent radius of $r\a=r\p/\sqrt{2}$, there could also be planets with 
true radii $r=r\p/\sqrt{2}$ orbiting singles, but there are no such systems 
in this model.

@@

The last item we need to write down the apparent rate density $\Gamma\a(r\a)$ 
is the number of unresolved point-sources on sky that the observer thinks are 
searchable, $N_\star$.
From the definition of $\mu$,
\begin{equation}
N_\star(r\a) = N_\star^0(r\a) \times (1 + \mu)
\label{eq:apparentlysearchable_to_searchable}
\end{equation}
relates the number of apparently searchable point-sources and the number of 
searchable singles.
There are in fact $N_\star^0(r\a)\times (1 + 2\mu)$ searchable stars
at any given $r\a$; the observers are under-counting.

Using Equation~\ref{eq:apparent_rate_density}, the apparent rate density 
reported when ignoring binarity is
\begin{align}
\Gamma\a(r\a) = 
\frac{1}{1+\mu} Z_0 \cdot
\delta(r\a-r\p)  +
\frac{\mu}{1+\mu} (Z_1 + Z_2) \cdot
\delta\left(r\a-\frac{r\p}{\sqrt{2}} \right).
\label{eq:model_1_apparent_rate_density}
\end{align}
The first term is from singles, and the second is from binaries.
The number of searchable singles at a given apparent radius, 
$N_\star^0(r\a)$, makes no appearance.
The observer has erred in Equation~\ref{eq:model_1_apparent_rate_density} by 
under-counting the number of searchable stars at any apparent radius, and by
inferring incorrect planet radii in binary systems.

@@

To assess the severity of these errors, we must assume both a binary fraction, 
and also the true number of planets per single, primary, and secondary star 
($Z_0,Z_1,Z_2$).
For the former,~\citet{raghavan_survey_2010} found a multiplicity 
fraction of 0.44 for primaries with masses from $0.7M_\odot$ to $1.3M_\odot$.
By multiplicity fraction, they meant ``fraction of systems in a volume-limited 
sample that are multiple'', which we simplistically conflate with the
fraction of systems in a volume-limited sample that are binaries:
\begin{equation}
{\rm binary\ fraction} \equiv \frac{n\b}{n\s + n\b} = 0.44,
\end{equation}
Of course not all of these are binaries are close to being ``twin'' binaries 
as we have assumed in our simple calculation.
Perhaps only a tenth of them have pairs of stars close enough
in their basic properties to produce errors as significant as those
we have been considering.  Thus, an appropriate estimate
for the binary fraction is of order $0.05$.
The ratio of the apparent to single star rate densities,
\begin{equation}
X_\Gamma(r) \equiv \left. \frac{\Gamma\a(r\a)}{\Gamma_0(r)} \right|_{r\a 
    \rightarrow r},
\end{equation}
can then be evaluated as a ``correction factor''.
At the true planet radius, $X_\Gamma(r\p)=1/(1+\mu)$.
This yields a correction $X_\Gamma$ of 0.87~(0.76) if the binary fraction is 
0.05~(0.10).
All together the various effects produce biases of order 10\% in the
occurrence rates.  We will see that this level of error is characteristic
of many of our more complicated models, as well.

An alternative assumption is that secondaries do not host planets. In that 
case, the correction to the rate density at the true planet radius becomes 
$X_\Gamma(r\p) = (1+2\mu)/(1+\mu)^2$.
This gives a correction of 0.98~(0.94) if the binary fraction is 0.05~(0.10).
Although the secondaries certainly should have planets, 
the sensitivity of $\Gamma\a/\Gamma_0$ to the relative number of
planets per single, primary, and secondary will also become important
as we proceed.

@@

A simple extension to the previous example helps distinguish 
between the apparent and underlying planet populations.
Consider now a universe that is the same as in
Section~\ref{sec:model_1}, except that half of planets have radii $r\p$, 
while the other half have radii $r\p/\sqrt{2}$.
The rate densities are
\begin{equation}
\Gamma_i(r) = \frac{Z_i}{2} \left[
\delta(r-r\p) + \delta\left(r-\frac{r\p}{\sqrt{2}}\right)
\right], \quad {\rm for}\  i \in \{ 0,1,2 \},
\end{equation}
where $i=0$ corresponds to singles, $i=1$ to primaries, and $i=2$ to
secondaries, and the $Z_i$'s are the number of planets per star of
each type.

Following an identical line of reasoning as in Section~\ref{sec:model_1}, the 
apparent rate density can be written
\begin{align}
\notag
\Gamma\a(r\a) &=
\frac{1}{2(1+\mu)} \left[
Z_0 \cdot \delta(r\a - r\p)
+
\left[Z_0 + \mu (Z_1 + Z_2)
\right] \cdot \delta\left(r\a - \frac{r\p}{\sqrt{2}}\right) 
\right. \\
&\quad\quad\quad\quad\quad\quad\quad\quad+
\left.
\mu(Z_1 + Z_2) \cdot \delta\left(r\a - \frac{r\p}{2}\right)
\right].
\label{eq:two_radii_twins}
\end{align}
Just as in Equation~\ref{eq:model_1_apparent_rate_density}, the
$N_\star^0(r\a)$ terms cancel, leaving only the $\mu$ weights.
However, there are now three detected planet sizes.
Also different is that two populations contribute at $r\a = 
r\p/\sqrt{2}$:
the first population is singles with $r=r\p/\sqrt{2}$, and the second is twin 
binaries with $r=r\p$.
Both populations are detected out to the same maximum searchable distance.
More generally, at any given apparent radius, there will be contributions
from both singles, primaries, and secondaries~---~but the relative weights
between these contributions will depend on the underlying occurrence rates.

@@

A derivation of Equation~\ref{eq:general_Gamma_a} is given in the 
\hyperref[sec:appendix]{Appendix}; its qualitative features are the same as 
from our simple model (Equation~\ref{eq:model_1_apparent_rate_density}).
The terms inside the curly braces $\{ \ldots \}$ are the sum of 
the apparent rate densities from singles, primaries, and secondaries.
The contribution from singles is not affected by binarity.
In the contributions from primaries and secondaries,
planets with $(r\a, M\a)$ are associated with 
systems of different planetary and stellar properties, as determined
by the mass ratio $q$ of each binary.
This corresponds to true planet radii and stellar masses 
$(r\a/\mathcal{A},M\a)$ for primaries, and $(r\a/\mathcal{B},qM\a)$ for 
secondaries.
These contributions are then integrated over the mass ratio distribution 
including the effect of Malmquist bias, $f(q)/\mathcal{A}^3$, discussed 
further below. Finally, the latter term in the apparent rate density of 
secondaries comes from a correction for the overestimated transit probability.

\paragraph{Ratio of searchable binaries to singles}
We must also specify the exact form of $\mu$, the ratio of 
the number of searchable binary systems to singles.
Given the observed signal $\delta_{\rm obs}$ and apparent stellar mass $M\a$, 
recall that the maximum searchable distances for singles and binaries are 
proportional to $\delta_{\rm obs}\cdot L(M\a)^{1/2}$ and $\delta_{\rm 
obs}\cdot [L(M\a)+L(qM\a)]^{1/2}$.
Applying Equation~\ref{eq:N_searchable_prop},
\begin{equation}
\mu({\rm BF},M\a) = 
\frac{N_\star^{\rm b}(r\a)}{N_s^0(r\a)}=
\int_0^1 {n_{\rm b}\over n_{\rm s}}\left[1+{L(qM\a) \over L(M\a)}\right]^{3/2} 
f(q)\,\mathrm{d}q.
\label{eq:mu_general}
\end{equation}
If the binary fraction is independent of $q$, $L \propto M^\alpha$, and $f(q) 
\propto q^\beta$, this simplifies to
\begin{equation}
\mu =\frac{{\rm BF}}{1 - {\rm BF}}\cdot {1\over{1+\beta}}\int_0^1 
\left(1+q^\alpha\right)^{3/2} q^\beta \,\mathrm{d}q.
\label{eq:mu_power_laws}
\end{equation}
%which can also be rewritten using the hypergeometric function.
\begin{figure}[!tb]
    \centering
    \includegraphics[width=0.6\textwidth]{figures/mass_ratio_distribution.pdf}
    \caption{
        The mass ratio distribution for a magnitude-limited sample of 
        binary stars, in which the underlying volume-limited distribution is 
        uniform, qualitatively similar to
        Figure~16 of \citet{raghavan_survey_2010}.
        At a given observed transit depth, the searchable binaries in a 
        transit survey are magnitude-limited.
    }
    \label{fig:q_distribn_mag_limited}
\end{figure}
This can be understood as a Malmquist bias: at fixed observed transit 
depth, for singles and primaries with the same luminosity, binaries are 
searchable to a greater distance.
Specifically, the sample of searchable binaries is magnitude-limited.
Given a searchable binary, the probability that it has a mass ratio $q$ 
scales as
\begin{equation}
p({\rm draw\ }q\,|\,{\rm system\ is\ binary}) \propto 
(1+q^\alpha)^{3/2} q^\beta 
\label{eq:Malmquist_bias}
\end{equation}
where $q^\beta$ is the volume-limited probability of drawing a binary of mass 
ratio $q$, and the first term is the Malmquist bias when $L\propto M^\alpha$.
We show this magnitude-limited mass ratio distribution for the $\beta=0$ case 
in Figure~\ref{fig:q_distribn_mag_limited}.
In Monte Carlo simulations of transit surveys, it is 
important to draw binaries from a correctly biased mass-ratio distribution 
\citep[\textit{e.g.},][]{bakos_hatsouth:_2013,sullivan_transiting_2015,
    gunther_new_2017}.
